### 2017-08-06 paper/incomeShocks-jde-r1.tex
Add contraceptive results table

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Contraceptive\\ Use Overall and By Type}
\label{tab:contraceptive}
\begin{tabular}{@{} l D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       &                     & \mct{Fixed Effects}                       \\ \cmidrule(lr){3-4} 
                                                       & \mco{OLS}           & \mco{Community}     & \mco{Woman}         \\ \midrule
                                                       &\multicolumn{3}{c}{Any contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &       0.061\sym{**} &       0.059\sym{**} &       0.070\sym{**} \\
                                                       &     (0.027)         &     (0.027)         &     (0.033)         \\
\addlinespace 
                                                       &\multicolumn{3}{c}{Traditional contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &       0.052\sym{**} &       0.048\sym{**} &       0.054\sym{**} \\
                                                       &     (0.023)         &     (0.022)         &     (0.024)         \\
\addlinespace 
                                                       &\multicolumn{3}{c}{Modern contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &      -0.001         &       0.004         &       0.003         \\
                                                       &     (0.014)         &     (0.013)         &     (0.020)         \\
\addlinespace                                                        
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community fixed effects                                &    \mco{No}         &    \mco{Yes}        &    \mco{No}         \\
Woman fixed effects                                    &    \mco{No}         &    \mco{No}         &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
All models are linear probability models.
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
% Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

% Table with contraceptive use results
\input{../tables/main_contraceptives.tex}
